\documentclass{article}

\usepackage{times}
\usepackage{uist}

\begin{document}

% --- Copyright notice ---
\conferenceinfo{UIST'09}{October 4-7, 2009, Victoria, British Columbia, Canada}
\CopyrightYear{2009}
\crdata{978-1-60558-745-5/09/10}

% Uncomment the following line to hide the copyright notice
 \toappear{}
% ------------------------

\bibliographystyle{plain}

\title{Automatically Generating Color Palettes\\for Categorical Values}

%%
%% Note on formatting authors at different institutions, as shown below:
%% Change width arg (currently 7cm) to parbox commands as needed to
%% accommodate widest lines, taking care not to overflow the 17.8cm line width.
%% Add or delete parboxes for additional authors at different institutions. 
%% If additional authors won't fit in one row, you can add a "\\"  at the
%% end of a parbox's closing "}" to have the next parbox start a new row.
%% Be sure NOT to put any blank lines between parbox commands!
%%

\author{
\parbox[t]{9cm}{\centering
	     {\em Chinmay Kulkarni}\\
	     Stanford University HCI Group\\
              Computer Science Department\\
	     Stanford, CA 94305\\
	     chinmay@cs.stanford.edu}
\parbox[t]{9cm}{\centering
	     {\em Julie Fortuna}\\
	     Stanford University HCI Group\\
              Computer Science Department\\
	     Stanford, CA 94305\\
	     jfortuna@stanford.edu}
}

\maketitle

\abstract
Is it possible to automatically create a color palette relevant to a topic? Could such a palette be used to guide color choices while visualizing data? We envision a tool that automatically creates aesthetically pleasing and topic-relevant palettes for a large class of topics. In order to do this, we must first extract palettes from color pixel values of images from Google Images via clustering and topic models. 

\classification{H5.2 [Information interfaces and presentation]:
User Interfaces. - Graphical user interfaces.}

\terms{Design, Human Factors, Experimentation}

\keywords{Information visualization, colors, crowdsourcing, user study}

\tolerance=400 
  % makes some lines with lots of white space, but 	
  % tends to prevent words from sticking out in the margin

\section{INTRODUCTION}
blah blah blah 

\section{RELATED WORK}
Prior work exists on automatic creation of color palettes. This work falls broadly in two categories. The first focuses on finding representative  colors from images, that can be used as color palettes. The most recent of these is~\cite{morse2007image}. This line of research has so far focused only on extracting colors from a single image. This project extends this work by extracting colors from multiple, related images. I believe that some of the techniques used by~\cite{morse2007image}, such as a weighted histogram that uses color saturation and neighborhood color coherence, can be adapted for multiple images too. Depending on constraints of time, I plan to explore some of these techniques.
	
The second category of research on palette generation focuses on optimizing visual properties, such as color saliency and perceptive color distance, both manual or rule-based, as pioneered by Brewer~\cite{brewer1999color}; and  with varying degrees of automation ~\cite{healey1996choosing, zeileis2009RGBland}. I believe most such optimization research is complementary to this project, and can be used as a post-extraction step to optimize the colors chosen. Statistical work on color saliency is valuable, even if it hasn't been directly applied as a optimization objective; color saliency in the context outside data-visualization in~\cite{chuang2008probabilistic, benavente2002statistical}. 

Topic models have been shown to be effective in information retrieval. Latent semantic analysis (and later, LDA), for instance, has been used to find ``latent'' similarities between concepts~\cite{dumais1988using, blei2003latent}. Similar similarity-measures have been computed for nodes in a graph~\cite{jeh2002simrank}. While these similarity measures may help to better cluster color-values, they don't target the domain of color recommendations directly. 

\section{SYSTEM DESIGN}
blah blah equations blah

\section{SYSTEM EVALUATION}
We evaluated the system on three related metrics: the likability of the generated color palettes, how topic-relevant the palettes were perceived to be, and how the colors in the palette affect understanding of the data they represent. For all three metrics, the algorithmically generated palettes were compared against a randomly generated palette, and one generated by experts. For the likability and understanding metrics, the random palette was chosen from the set of palettes generated for other topics by our system. This was to ensure that only the relevance, not the base quality of the colors was considered. For all topics tested, we limited the number of specific items represented in the palette to four. This also allowed us to compare the algorithmically and randomly generated palettes to the randomly generated palettes. We ran a small laboratory study of X participants recruited through school mailing lists, in addition to a large-scale crowdsourced study on Amazon's Mechanical Turk. 

\subsection{Likability}
To measure likability, the automatically, expert, and randomly generated color palettes for a given topic are presented in a random order. Participants rate each palette on a seven-point Likert scale based on how much they like each palette for a given topic. 

\subsection{Relevance}
For relevance, an association task is used: given a topic (e.g "US Politics") and one of the topic terms (e.g. "Democrat"), the participant chooses which color, among a set of displayed swatches, is relevant to it.

\subsection{Understanding}
For understanding, users will be shown differently-colored infographics, and participants will be timed while they answer conceptual questions related to the infographic. Since the three metrics may interact strongly, they will be studied in a within-subjects design.

\section{RESULTS}
blah blah

\section{DISCUSSION}
blah

\section{CONCLUSION}
blah

\section{ACKNOWLEDGMENTS}
\begin{center}
\textbf{This section should be left blank for blind review}
\end{center}

The authors would like to acknowledge the contributions of many previous
editors in the writing and formatting of this document.  This document is based on
the {\em CHI '94} format-ting guidelines.

%%%	You can use bibtex if you like, but I've hardwired in these 
%%%	references to avoid sending you a separate .bib file.
\begin{thebibliography}{9}

\bibitem{ACMTerms} How to Classify Works Using ACMÕs Computing
Classification System. {http://www.acm.org/class/how\_to\_use.html}.

\bibitem{badenov91}  Badenov, B. Effects of prolonged use of WIMP user
interfaces on Alces americana and Glaucomys volans.
In {\em Proceedings of UIST '87}
(February 30--April 1, Graceland, TN), ACM, NY, 1987, pp. 231--240.

\bibitem{henry-etal92} Henry, T.R., Yeatts, A.K., Hudson, S.E., Myers, B.A.,
and Feiner, S.K.  A nose gesture interface device: Extending virtual realities.
{\em Presence 1}, 2 (Spring 1992), 258--261.

\bibitem{GenderNeutral} Schwartz, M. Guidelines for Bias-Free Writing.
Indiana University Press, Bloomington, IN, USA, 1995.

\bibitem{zaranka81} Zaranka, W., Ed. {\em The Brand-X Anthology of Poetry:  A
Parody Anthology.}  Apple-wood Books, Cambridge, MA, 1981.
\end{thebibliography}

\end{document}